SAT Competition 2020\tnoteref{title}

### 2021-02-02 paper/main.tex

All the winning solvers of the \emph{Main} track periodically schedule runs of an SLS solver and import statistical information generated in unsuccessful SLS runs to reconfigure weights in their branching heuristics.

As can be seen in the \emph{Parallel} track, it is hard to scale SAT solving beyond $32$ threads, as in some occasions the $32$ threaded version of the same solver outperformed its $64$ threaded counterpart. 
However, from the winner in the massively parallel \emph{Cloud} track, we can learn that classic all-to-all clause-sharing can be outperformed by a more sophisticated clause-sharing architecture.

It is hard to integrate and test sophisticated state-of-the-art methods in an incremental SAT solver and thus solvers usually disable parts of their features in the incremental use-case. 
The winner of the \emph{Incremental Library} track showed that it is worth integrating a full solver functionality in the incremental use-case.

\subsection*{Future Competitions}

>>>>

The 2020 SAT Competition successfully continued the tradition of the SAT Competition series. In 2020, significant advances
in SAT solver compared to previous years were observed. Some of the more interesting observations on the winning solving 
strategies include the following.
All the winning solvers of the \emph{Main} track periodically schedule runs of a stochastic local search (SLS)
solver and import statistical information generated in unsuccessful SLS runs to reconfigure weights in their branching heuristics. As can be seen in the \emph{Parallel} track, it appear difficult to make proper use of more that $32$ threads for SAT solving, as in some occasions the $32$-threaded version of the same solver outperformed its $64$ threaded counterpart. 
However, from the winner in the massively parallel \emph{Cloud} track, we can learn that classic all-to-all clause-sharing can be outperformed by a more sophisticated clause-sharing architecture. 
It is hard to integrate and test sophisticated state-of-the-art methods in an incremental SAT solver and thus solvers usually disable parts of their features in the incremental use-case. 
The winner of the \emph{Incremental Library} track showed that it is worth integrating a full solver functionality in the incremental use-case.

\subsection*{Future Prospects}
